---
title: "Week 5 Visualizations Activity"
author: "Grace Zeng"
date: "6/23/2024"
output:
  html_document: null
  theme: journal
  pdf_document: default
---

### Description of the data：
The dataset* selected for this analysis comes from the FBI and the Southern Poverty Law Center (SPLC) and the research question is: What are the trends in hate crime rates by state, and what state-level factors are associated with these variations?

Data collection: The federal government does not systematically track hate crimes, as reporting to the FBI is voluntary. The Southern Poverty Law Center relies on media accounts and self-reports to evaluate the situation. Both sources provide publicly available data.

*The dataset is found on [GitHub](https://github.com/fivethirtyeight/data/tree/master/hate-crimes)
 and it is in csv. format.  More background information can be found in this [article](https://fivethirtyeight.com/features/higher-rates-of-hate-crimes-are-tied-to-income-inequality/).


---


```{r setup, include= FALSE}
knitr::opts_chunk$set(echo = TRUE)

#install.packages("tidyverse")

library(tidyverse)
```

```{r GitHubdata, include= FALSE}
#task 2: Loading the data：
url <- "https://raw.githubusercontent.com/fivethirtyeight/data/master/hate-crimes/hate_crimes.csv"
hate_crimes <- read_csv(url)
glimpse(hate_crimes)
```

Histogram: 
```{r histogram, echo = FALSE}
ggplot(hate_crimes, aes(x=median_household_income)) + 
  geom_histogram()
```

Bar chart: 

```{r bar, echo = FALSE }
ggplot(data = hate_crimes, aes(x = state, y = median_household_income)) +
  geom_bar(stat = "identity") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(title = "Median Household Income by State",
       x = "State",
       y = "Median Household Income")

```

Correlation plot: median_household_income and avg_hatecrimes_per_100k_fbi
```{r cor, echo = FALSE }
ggplot(data = hate_crimes) +
  geom_point(mapping = aes(x = median_household_income, y = avg_hatecrimes_per_100k_fbi))
```

Correlation plot: median_household_income and share_population_with_high_school_degree

```{r cor2, echo = FALSE }
ggplot(data = hate_crimes) +
  geom_point(mapping = aes(x = median_household_income, y = share_population_with_high_school_degree))
```
